О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-01 pps-linear-bound/pps-linear-lower-bound.tex
Add motivation for a conjecture

>>>>

The motivation of Conjecture~\ref{con:no_optimal_with_edge_1} is based on the results of~\cite[Section 5]{kurz2008minimum},
especially the following theorem.

\begin{theorem}
	For every $12 \leq n \leq 122$, there exist a facher optimal sets $M_n\in\mathfrak{M}(2,n)$
	that consist of $n-1$ points $\{ (b_1,0), ..., (b_{n-1},0)\}$
	and the point $(0,\sqrt{A_n})$,
	where $b_1,...,b_{n-1}, A_n$ are integer and $\sqrt{A_n}\notin\mathbb{N}$.
\end{theorem}
Such a set can not contain distance 1: due to Theorem~\ref{thm:minimeter_1_planar} below,
the points with distance 1 should be $(\pm 1/2, 0)$.
